Current State of Knowledge Representation Systems for Robotics

### 2011-11-25 krs-survey.tex
Rewrite paragraph on presupposition accomodation to be more accurate

Another important application of non-monotonic reasoning is representation of
change: for example, to make an omelette, you need to crack eggs and wipe them.
The eggs disappear and are replaced by an omelette:

$Egg(a) \wedge Egg(b) \wedge MakeOmelette(a, b, c) \to \lnot Egg(a) \wedge
\lnot Egg(b) \wedge Omelette(c)$

The insertion of the proposition $MakeOmelette(a, b, c)$ leads to retraction of
other facts. This rule requires non-monotonic reasoning to be applied.

@@

>>>>

@@

\paragraph{Representation of change}

E.g. \emph{"The pancake dough disappears into a pancake"}
